Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2021-03-04 manuscript.tex
Replace section title to make it more precise [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/5e807b16ac2e386569de57f32a6678be4e8a29d2.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/5e807b16ac2e386569de57f32a6678be4e8a29d2/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/621638436

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...6585a9f107bab6576e117b3f6d20504cc14fc9d3}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/6585a9f107bab6576e117b3f6d20504cc14fc9d3/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/6585a9f107bab6576e117b3f6d20504cc14fc9d3}{habi/zmk-tooth-cohort-method-manuscript@6585a9f}
on March 4, 2021.

@@

One hundred and four human teeth were scanned on a high-resolution micro-CT scanner susing an automatic specimen changer.
Python code in a Jupyter notebook was used to verify and process the scans, prepare the datasets for description of the internal morphology and to measure the apical region of the tooth.

@@

\hypertarget{detection-of-enamel-dentin-border}{%
\paragraph{Detection of enamel-dentin border}\label{detection-of-enamel-dentin-border}}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...5e807b16ac2e386569de57f32a6678be4e8a29d2}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/5e807b16ac2e386569de57f32a6678be4e8a29d2/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/5e807b16ac2e386569de57f32a6678be4e8a29d2}{habi/zmk-tooth-cohort-method-manuscript@5e807b1}
on March 4, 2021.

@@

One hundred and four human teeth were scanned on a high-resolution micro-CT scanner using an automatic specimen changer.
Python code in a Jupyter notebook was used to verify and process the scans, prepare the datasets for description of the internal morphology and to measure the apical region of the tooth.

@@

\hypertarget{root-canal-system-classification}{%
\paragraph{Root canal system classification}\label{root-canal-system-classification}}
